Interactive dashboard to monitor the COVID-19 outbreak

### 2022-04-22 manuscript_covid19dashboard.Rmd
Updated

### Summary of data representation on dashboards

@@

### 2.2 Comparison of Dashboards

@@

As shown in table 04 almost each & every dashboard, line charts & bar charts have been used to visualize the data. Heat map & dot plot has been used only one dashboard. Only four dashboards have been fitted with a single screen. The majority of dashboards have used color theme on the whole dashboard. That is, dashboards have been applied different colors for different type of data (i.e. One specific color for confirmed cases, another color for deaths, etc.) in the whole dashboard. The data set & related links have available on some dashboards & users can download these data sets. There are 6 dashboards with dark background while others have been used light background. Last updated time & date of the latest available data  has been reported at the top or bottom of the first panel in the dashboard. Like, half of dashboards included all data in one panel.

@@

Table 5 provides an overview of methods that have been used to visualize data.

>>>>

## Summary of data representation on dashboards

@@

## 2.2 Comparison of Dashboards

@@

As shown in Table 4 almost each & every dashboard, line charts & bar charts have been used to visualize the data. Heat map & dot plot has been used only one dashboard. Only four dashboards have been fitted with a single screen. The majority of dashboards have used color theme on the whole dashboard. That is, dashboards have been applied different colors for different type of data (i.e. One specific color for confirmed cases, another color for deaths, etc.) in the whole dashboard. The data set & related links have available on some dashboards & users can download these data sets. There are 6 dashboards with dark background while others have been used light background. Last updated time & date of the latest available data  has been reported at the top or bottom of the first panel in the dashboard. Like, half of dashboards included all data in one panel.

@@

In this study, we have daily COVID-19 data related to deaths, recovered and confirmed cases in all 25 districts in Sri Lanka. This structure generates a multiple time series collection. Visualizing these time series data is useful to identify similarities and dissimilarities between districts and their general trends. There are two approaches to visualizing these time series: (i) drawing individual time series plots for each district, and (ii) simultaneously plots all time series on a single panel. Plotting separate panels for each district is not effective. The reason is that it is hard to compare across 25 different panels at once. Plotting all time series simultaneously is also not possible due to overlapping time series and scale differences. We use heatmaps  to visualize global and local similarities and dissimilarities across districts (@peng2008method) along with Tree Maps, Choropleth Maps, and  Dorling Cartogram. The cumulative number of confirmed deaths, and confirmed cases (both on log scale and linear scale) were used to compare the status of Sri Lanka against the top-10 countries affected by COVID-19. Furthermore, we use color-blind friendly colour palettes for the graphics. To represent qualitative data, a diverging colour palette was used, and to represent numeric variables, a sequential colour theme was used. Table 5 provides an overview of methods that have been used to visualize data.

### 2022-04-22 manuscript_covid19dashboard.tex
Updated

\hypertarget{summary-of-data-representation-on-dashboards}{%
\subsubsection{Summary of data representation on
dashboards}\label{summary-of-data-representation-on-dashboards}}

@@

\hypertarget{comparison-of-dashboards}{%
\subsubsection{2.2 Comparison of
Dashboards}\label{comparison-of-dashboards}}

@@

As shown in table 04 almost each \& every dashboard, line charts \& bar
charts have been used to visualize the data. Heat map \& dot plot has
been used only one dashboard. Only four dashboards have been fitted with
a single screen. The majority of dashboards have used color theme on the
whole dashboard. That is, dashboards have been applied different colors
for different type of data (i.e.~One specific color for confirmed cases,
another color for deaths, etc.) in the whole dashboard. The data set \&
related links have available on some dashboards \& users can download
these data sets. There are 6 dashboards with dark background while
others have been used light background. Last updated time \& date of the
latest available data has been reported at the top or bottom of the
first panel in the dashboard. Like, half of dashboards included all data
in one panel.

@@

Table 5 provides an overview of methods that have been used to visualize
data.

@@

>>>>

\hypertarget{summary-of-data-representation-on-dashboards}{%
\subsection{Summary of data representation on
dashboards}\label{summary-of-data-representation-on-dashboards}}

@@

\hypertarget{comparison-of-dashboards}{%
\subsection{2.2 Comparison of
Dashboards}\label{comparison-of-dashboards}}

@@

As shown in Table 4 almost each \& every dashboard, line charts \& bar
charts have been used to visualize the data. Heat map \& dot plot has
been used only one dashboard. Only four dashboards have been fitted with
a single screen. The majority of dashboards have used color theme on the
whole dashboard. That is, dashboards have been applied different colors
for different type of data (i.e.~One specific color for confirmed cases,
another color for deaths, etc.) in the whole dashboard. The data set \&
related links have available on some dashboards \& users can download
these data sets. There are 6 dashboards with dark background while
others have been used light background. Last updated time \& date of the
latest available data has been reported at the top or bottom of the
first panel in the dashboard. Like, half of dashboards included all data
in one panel.

@@

In this study, we have daily COVID-19 data related to deaths, recovered
and confirmed cases in all 25 districts in Sri Lanka. This structure
generates a multiple time series collection. Visualizing these time
series data is useful to identify similarities and dissimilarities
between districts and their general trends. There are two approaches to
visualizing these time series: (i) drawing individual time series plots
for each district, and (ii) simultaneously plots all time series on a
single panel. Plotting separate panels for each district is not
effective. The reason is that it is hard to compare across 25 different
panels at once. Plotting all time series simultaneously is also not
possible due to overlapping time series and scale differences. We use
heatmaps ~to visualize global and local similarities and dissimilarities
across districts (Peng (2008)) along with Tree Maps, Choropleth Maps,
and ~Dorling Cartogram. The cumulative number of confirmed deaths, and
confirmed cases (both on log scale and linear scale) were used to
compare the status of Sri Lanka against the top-10 countries affected by
COVID-19. Furthermore, we use color-blind friendly colour palettes for
the graphics. To represent qualitative data, a diverging colour palette
was used, and to represent numeric variables, a sequential colour theme
was used. Table 5 provides an overview of methods that have been used to
visualize data.

@@

\leavevmode\hypertarget{ref-peng2008method}{}%
Peng, Roger D. 2008. {``A Method for Visualizing Multivariate Time
Series Data.''}
